04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
back to working

  # LDA plot using ggplot2 
  lda.data <- cbind(train.transformed, predict(model)$x)
  p<-ggplot(data=lda.data, aes(x=treatment, y=LD1, fill = treatment)) +
    geom_bar( stat = "summary", fun.y = "mean")
  plot(p)

>>>>

  # LDA plot using ggplot2 
  lda.data <- cbind(train.transformed, predict(model)$x)
  p <- ggplot(data=lda.data, aes(x=treatment, y=LD1, fill = treatment)) +
    geom_bar( stat = "summary", fun.y = "mean")
  plot(p)
